\documentclass[DIV16,twocolumn,10pt]{scrreprt}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage[final]{hcar}

\begin{document}

\begin{hcarentry}{haskell-ide-engine, a project for unifying IDE functionality}
\report{Chris Allen}
\status{Open source, just beginning}
\participants{Alan Zimmerman, Michael Sloan, Gracjan Polak, Daniel Gr\"ober, others welcome}

\makeheader

\textit{haskell-ide} is a backend for driving the sort of features programmers
expect out of IDE environments. Perhaps soon to be called
\textit{haskell-ide-engine}, \textit{haskell-ide} is a project to unify tooling
efforts into something different text editors, and indeed IDEs as well, could
use to avoid duplication of effort.

Features like type errors, linting, refactoring, and reformatting code are
planned. People who are familiar with a particular part of the chain can
focus their efforts there, knowing that the other parts will be handled by
other components of the backend. Inspiration is being taken from the work the
Idris community has done toward an interactive editing environment as well. This
is a deliberately broad scope, the initial versions will be very limited at
first. The sooner we can get started the sooner we will have something concrete
to criticise and improve.

Help is very much needed and wanted so if this is a problem that interests you,
please pitch in! This is not a project just for a small inner circle. Anyone
who wants to will be added to the project on github, address your request to
@alanz or @hvr.

\FurtherReading
  \url{https://github.com/haskell/haskell-ide-engine} \\
  \url{https://mail.haskell.org/pipermail/haskell-cafe/2015-October/121875.html} \\
  \url{https://www.fpcomplete.com/blog/2015/10/new-haskell-ide-repo} \\
  \url{https://www.reddit.com/r/haskell/comments/3pt560/ann_haskellide_project/} \\
  \url{https://www.reddit.com/r/haskell/comments/3qbgmo/fp_complete_the_new_haskellide_repo/}

\end{hcarentry}

\end{document}
