% haskellideengineaprojectf-Ch.tex
\begin{hcarentry}{haskell-ide-engine, a project for unifying IDE functionality}
\label{haskell-ide-engine}
\report{Chris Allen}%11/15
\status{Open source, just beginning}
\participants{Alan Zimmerman, Moritz Kiefer, Michael Sloan, Gracjan Polak, Daniel Gr\"ober,
others welcome}

\makeheader

\textit{haskell-ide-engine} is a backend for driving the sort of features programmers
expect out of IDE environments. \textit{haskell-ide-engine} is a project to unify tooling
efforts into something different text editors, and indeed IDEs as well, could
use to avoid duplication of effort.


There is basic support for getting type information and refactoring,
more features including type errors, linting and reformatting are
planned. People who are familiar with a particular part of the chain
can focus their efforts there, knowing that the other parts will be
handled by other components of the backend. Integration for Emacs and
Leksah is available and should support the current features of the
backend. \texttt{haskell-ide-engine} also has a REST API with Swagger UI.
Inspiration is being taken from the work the Idris community has done
toward an interactive editing environment as well.

Help is very much needed and wanted so if this is a problem that interests you,
please pitch in! This is not a project just for a small inner circle. Anyone
who wants to will be added to the project on github, address your request to
@alanz.

\FurtherReading
\begin{compactitem}
\item\url{https://github.com/haskell/haskell-ide-engine}
\item\url{https://mail.haskell.org/pipermail/haskell-cafe/2015-October/121875.html}
\item\url{https://www.fpcomplete.com/blog/2015/10/new-haskell-ide-repo}
\item\url{https://www.reddit.com/r/haskell/comments/3pt560/ann_haskellide_project/}
\item\url{https://www.reddit.com/r/haskell/comments/3qbgmo/fp_complete_the_new_haskellide_repo/}
\end{compactitem}

\end{hcarentry}
